Using temperature distributions of active regions to investigate flare activity

### 2015-01-27 paper.tex
Massive table of flares added
Tracking description added

@@

\begin{table}
	\centering
		\begin{tabular}

>>>>

The Paper I method also allows easy 'tracking' of solar regions by cropping the temperature map around a set of Carrington heliographic coordinates, which rotate at approximately the rate of solar rotation.
This tracking is demonstrated in Figures A, B and C, each of which shows a cropped region of an AIA 17.1nm image containing active region AR11185, the corresponding temperature map and a larger 17.1nm image showing the location of the region in the corona.

@@

\begin{table}
	\centering
		\begin{tabular}{c|c|c}
			Date and time & GOES class & NOAA Active region \\
			\hline
